Biden Projected to Win in the 2024 US Presidential Election

### 2024-03-15 paper/paper.qmd
poststrat modifications

state_vote_for_biden <- read.csv(here("output", "state_vote_for_biden.csv"))

age_vote_for_biden <- read.csv(here("output", "age_vote_for_biden.csv"))

sex_vote_for_biden <- read.csv(here("output", "sex_vote_for_biden.csv"))

general_data <- read.csv(here("output", "general_vote_for_biden.csv"))

>>>>

state_vote_for_biden <- read.csv(here("data/poststratified/state_vote_for_biden.csv"))
age_vote_for_biden <- read.csv(here("data/poststratified/age_vote_for_biden.csv"))
sex_vote_for_biden <- read.csv(here("data/poststratified/sex_vote_for_biden.csv"))
general_data <- read.csv(here("data/poststratified/general_vote_for_biden.csv"))
